\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{classic} % options: 'casual', 'classic', 'banking'
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.9]{geometry}

% Personal data
\name{Allen}{Hart}
\address{University of Warwick}{Coventry, UK}
\email{allen.hart@warwick.ac.uk}
%\homepage{scholar.google.com/citations?user=XXXXX} % link to Google Scholar

\begin{document}
\makecvtitle

%----------------------------------------------------------------------------------
% Education
%----------------------------------------------------------------------------------
\section{Education}
\cventry{2017--2021}{PhD in Statistical and Applied Mathematics}{University of Bath}{Bath, UK}{}%
{Thesis on neural networks and dynamical systems; focus on recurrent neural networks, reservoir computing, and embedding theorems.}
\cventry{2013--2017}{MSci Mathematics and Physics (1st Class Honours)}{University of Bath}{Bath, UK}{}{}
\cventry{2011--2013}{A-Levels}{Slough Grammar School}{Slough, UK}{}{Mathematics (A*), Further Mathematics (A*), Physics (A), History (AS, A)}

%----------------------------------------------------------------------------------
% Research and Professional Experience
%----------------------------------------------------------------------------------
\section{Research and Professional Experience}
\cventry{Present}{Innovation Research Associate}{University of Warwick}{Coventry, UK}{}{
\begin{itemize}
  \item Algorithms and infrastructure for \textbf{vector similarity search}.
  \item Developing software for \textbf{battery optimisation}
\end{itemize}}

\cventry{2023--2024}{Research Fellow, Project Bluebird}{University of Exeter / Alan Turing Institute / NATS}{Exeter, UK}{}{
\begin{itemize}
  \item Collaboration between the Turing institute, Exeter University, and NATS to \textbf{automate air traffic control}.
\end{itemize}}

\cventry{2022}{Data Science Intern}{Spectra Analytics (Patchs Health)}{London, UK}{}{
\begin{itemize}
  \item Deployed ML models for healthcare applications.
\end{itemize}}

\cventry{2015--2016}{Research Intern}{Institut Laue–Langevin}{Grenoble, France}{}{
\begin{itemize}
  \item Studying the diffraction of neutrons through ice and graphite surfaces.
\end{itemize}}

%----------------------------------------------------------------------------------
% Teaching & Pedagogy
%----------------------------------------------------------------------------------
\section{Teaching Experience}
%\cventry{2017--2025}{Ski Instructor}{Whistler (Canada), Zermatt (Switzerland), Interski (Italy), Selwyn (Australia)}{}{}{
%Achieved BASI Level 4 Teach \& IMS and CSIA Level 3. Delivered learner-led lessons internationally and completed pedagogical exams including peer review of teaching. Experienced in adapting instruction to diverse learner goals, confidence levels, and cultural backgrounds.}
\cventry{2022}{Postgraduate Teaching Assistant}{University of Bath}{Bath, UK}{}{Delivered online MSc module on neural networks and imaging; supervised assignments and critical reviews of recent ML papers.}
\cventry{2017--2021}{Undergraduate Mathematics Tutor}{University of Bath}{Bath, UK}{}{600+ hours tutoring mathematics and computer science undergraduates.}
\cventry{2018--2021}{Private Mathematics and Science Tutor}{TutorFair, Ivy Education}{UK}{}{200+ hours tutoring GCSE and A-level students in maths, physics, and further maths.}

%----------------------------------------------------------------------------------
% Publications
%----------------------------------------------------------------------------------
\section{Publications}
\cvitem{2025}{\textbf{Hart, A.G.} Generic and isometric embeddings in reservoir computers. \emph{Chaos: An Interdisciplinary Journal of Nonlinear Science}, 35(11), 111103.}
\cvitem{2024}{\textbf{Hart, A.G.} Generalised synchronisations, embeddings, and approximations for continuous time reservoir computers. \emph{Physica D: Nonlinear Phenomena}, 458, 133956.}
\cvitem{2023}{Grigoryeva, L., \textbf{Hart, A.}, Ortega, J.P. Learning strange attractors with reservoir systems. \emph{Nonlinearity}, 36(9), 4674.}
\cvitem{2022}{\textbf{Hart, A.G.} Reservoir Computing with Dynamical Systems. PhD Thesis, University of Bath.}
\cvitem{2021}{Grigoryeva, L., \textbf{Hart, A.}, Ortega, J.P. Chaos on compact manifolds: Differentiable synchronizations beyond the Takens theorem. \emph{Physical Review E}, 103(6), 062204.}
\cvitem{}{\textbf{Hart, A.G.}, Hook, J.L., Dawes, J.H.P. Echo state networks trained by Tikhonov least squares are $L^2(\mu)$ approximators of ergodic dynamical systems. \emph{Physica D: Nonlinear Phenomena}, 421, 132882.}
\cvitem{}{Burridge, H.C., Bhagat, R.K., Stettler, M.E.J., Kumar, P., De Mel, I., Demis, P., \textbf{Hart, A.}, et al. The ventilation of buildings and other mitigating measures for COVID-19: a focus on wintertime. \emph{Proceedings of the Royal Society A}, 477(2247), 20200855.}
\cvitem{}{\textbf{Hart, A.G.}, Olding, K.R., Cox, A.M.G., Isupova, O., Dawes, J.H.P. Using echo state networks to approximate value functions for control. \emph{arXiv preprint arXiv:2102.06258}.}
\cvitem{2020}{\textbf{Hart, A.}, Hook, J., Dawes, J. Embedding and approximation theorems for echo state networks. \emph{Neural Networks}, 128, 234--247.}
\cvitem{2019}{\textbf{Hart, A.G.}, Hansen, T.C., Kuhs, W.F. A hidden Markov model for describing turbostratic disorder applied to carbon blacks and graphene. \emph{Acta Crystallographica Section A}, 75(3), 501--516.}
\cvitem{2018}{\textbf{Hart, A.G.}, Hansen, T.C., Kuhs, W.F. A Markov theoretic description of stacking-disordered aperiodic crystals including ice and opaline silica. \emph{Acta Crystallographica Section A}, 74(4), 357--372.}

%----------------------------------------------------------------------------------
% Conferences
%----------------------------------------------------------------------------------
\section{Selected Conference Talks}
\cvitem{2023}{International Congress on Industrial and Applied Mathematics (Tokyo) — Learning Strange Attractors with Reservoir Systems.}
\cvitem{2022}{Differential Equations for Data Science (Online) — Embedding and Approximation with Reservoir Computing.}
\cvitem{2021}{SIAM Conference on Applications of Dynamical Systems (Online) — Time Series Forecasting with Reservoir Computing.}

%----------------------------------------------------------------------------------
% Service
%----------------------------------------------------------------------------------
\section{Service}
\cvitem{}{Reviewer for: \emph{IEEE TNNLS}, \emph{Neural Networks}, \emph{Physica D}, \emph{Physical Review E}, \emph{Chaos}, \emph{SIAM J. Applied Mathematics}, \emph{Journal of Computational Physics}, \emph{Springer Nature}}

\end{document}
